\documentclass[12pt,a4paper,leqno]{report}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
 
\usepackage[ansinew]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[finnish]{babel}
\usepackage{amsthm}
\usepackage{amsfonts}         
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{lgreek}
\usepackage{multicol}



\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\No}{\mathbb{N}_0}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\diam}{\operatorname{diam}}

\theoremstyle{plain}
\newtheorem{lause}[equation]{Lause}
\newtheorem{lem}[equation]{Lemma}
\newtheorem{prop}[equation]{Propositio}
\newtheorem{kor}[equation]{Korollaari}

\theoremstyle{definition}
\newtheorem{maar}[equation]{Määritelmä}
\newtheorem{konj}[equation]{Konjektuuri}
\newtheorem{esim}[equation]{Esimerkki}

\theoremstyle{remark}
\newtheorem{huom}[equation]{Huomautus}

\pagestyle{plain}
\setcounter{page}{1}
\addtolength{\hoffset}{-1.15cm}
\addtolength{\textwidth}{2.3cm}
\addtolength{\voffset}{0.45cm}
\addtolength{\textheight}{-0.9cm}

\title{\textbf{Rio-projekti: Kuvankäsittely}}
\author{Tero Huomo, Eeva Terkki, Jussi Kirjavainen ja Niko Ahonen}
\date{25. maaliskuuta 2012}

\begin{document}

\maketitle

\tableofcontents
\listoffigures

\chapter{Johdanto}\label{johd}

\section{Alkusanat}
Teemu Kerola luennoi keväällä 2012 Helsingin yliopiston tietojenkäsittelytieteen laitoksella kurssin \textit{Rinnakkaisohjelmointi}. Kolmasosa kurssin arvosanasta muodostuu pienryhmissä tehtävästä projektityöstä. Tämä työ on ryhmämme projektityön dokumentointi.

\section{Tehtävän määrittely}
Kuudesta mahdollisesta projektityön aiheesta (liite \ref{A}) ryhmämme valitsi kuvankäsittelyyn liittyvän aiheen \textit{Image processing for ppm images}. Tässä tehtävänä oli ensin sumentaa annettua ppm-muotoista kuvaa kolme kertaa ja sitten tarkentaa sitä kolme kertaa. Tehtävän tulosteesta piti ilmetä vähintään:

\begin{itemize}
\item Kuvankäsittelyyn kulunut aika
\item Käytettyjen prosessorien ja säikeiden lukumäärä
\item Prosessoitu kuva tallennettuna samalla formaatilla kuin alkuperäinen
\end{itemize}

\chapter{Ohjelma}

\section{Toimintaperiaate}

\section{Luokat}

\subsection{Bitop.java}

\subsection{ImageProcessingMain.java}

\subsection{PixelImage.java}

\subsection{PpmImageParser.java}

\chapter{Testaus}

\section{Testauksen päämäärät}

\section{Testiluokat}

\subsection{BitopTest.java}

\chapter{Yhteenveto}





\appendix
\chapter{Projects}\label{A}

\begin{itemize}
\item \textbf{Sorting integers(to ascending order)}
\begin{itemize}
\item Minimum outputs:
\begin{itemize}
\item Time used to sort the integers
\item Amount of threads/processors used
\end{itemize}
\end{itemize}
\begin{itemize}
\item Performance competition data set is $/fs-1/2/kerola/rio$\_$testdata/ \\ uint64-keys.bin$  (64 bit  little-endian unsigned integers, 58M values, file size 0.47 GB; read from file server, do not make extra copies and waste space...)
\begin{itemize}
\item In 2011 best time was 1,72 s (Java)
\end{itemize}
\end{itemize}
\begin{itemize}
\item Java does not support well 64 bit unsigned integers. You may interpret the data set as signed integers instead.
\end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{ Sorting strings(to ascending order)}
\begin{itemize}
\item Minimum outputs:
\begin{itemize}
\item Time used to sort the strings
\item Amount of threads/processors used
\end{itemize}
\end{itemize}
\begin{itemize}
\item Performance competition data set is $/fs-1/2/kerola/rio$\_$testdata/utf-8-keys.txt$  (8 bit utf, 58M lines, file size 0.74 GB; read from file server, do not make extra copies and waste space...)
\begin{itemize}
\item In 2011 best time was 98 s (Java)
\end{itemize}
\end{itemize}
\end{itemize}

\clearpage

\begin{itemize}
\item \textbf{Matrix multiplication}
\begin{itemize}
\item Minimum outputs:
\begin{itemize}
\item Time used to multiply matrices
\item Amount of threads/processors used
\end{itemize}
\end{itemize}
\begin{itemize}
\item Performance competition data set consists of text file matrixes 
\begin{itemize}
\item $/fs-1/2/kerola/rio$\_$testdata/matr1$\_$7500.txt$
\item $/fs-1/2/kerola/rio$\_$testdata/matr2$\_$7500.txt$ 
\item In 2011 best time was 66,6 s (Java)
\end{itemize}
\end{itemize}
\begin{itemize}
\item Data set is given as two text files, each holding one matrix. Both files start with decimal integer N denoting the array size and followed by NxN array in row wise order (single accuracy floating points), values separated with white space. E.g.,
\begin{itemize}
\item file 1:   3    1.23 3.45 6.78    2.23 1.45 5.78   5.23 5.45 5.78 
\item file 2:   3    1.33 3.35 6.38    2.33 1.35 5.38   5.33 5.35 5.38  
\end{itemize}
\end{itemize}
\begin{itemize}
\item Tommi Tuura made 2 practice matrices for testing purposes. These files are only to aid the development of your program, they are not substitutes for the larger matrices in any way:
\begin{itemize}
\item $/fs-1/2/kerola/rio$\_$testdata/matr1$\_$1000.txt $
\item $/fs-1/2/kerola/rio$\_$testdata/matr2$\_$1000.txt $ 
\end{itemize}
\end{itemize}
\end{itemize}



\begin{itemize}
\item \textbf{Game of life}
\begin{itemize}
\item Minimum outputs:
\begin{itemize}
\item Time used to evolve all steps of life from the grid
\item Amount of threads/processors used
\item Final state of the grid saved in a file in same format as competition data set (in this file, the second integer should denote the number of steps that have been run)
\end{itemize}
\end{itemize}
\begin{itemize}
\item Performance competition data set (grid size NxN, nr of steps P, starting state) is $/fs-1/2/kerola/rio$\_$testdata/life$\_$800$\_$10000.txt$ (800x800 matrix, 10000 steps).
\begin{itemize}
\item Best time was 17,5 s (Java)
\end{itemize}
\end{itemize}
\begin{itemize}
\item Data set is given as a text file with integers N, P, NxN grid in row wise order (1 = alive, 0 = dead), values separated with white space
\begin{itemize}
\item \begin{verbatim} E.g., 4 20    0 0 0 0   0 1 0 0    0 0 1 0      0 0 0 0
\end{verbatim}
\end{itemize}
\end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{Image processing for ppm images}
\begin{itemize}
\item Minimum outputs:
\begin{itemize}
\item Time used to process the image as required
\item Amount of threads/processors used
\item The processed final result image saved in a file in same format as competition data set
\end{itemize}
\end{itemize}
\begin{itemize}
\item Performance competition data set is $/fs-1/2/kerola/rio$\_$testdata/ \\ 7976x4480.ppm$ with operations {smoothen, smoothen, smoothen, sharpen, sharpen, sharpen}. 
\begin{itemize}
\item in 2011 best time was 2,1 s (Java)
\end{itemize}
\end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{n-Queens (find all solutions)}
\begin{itemize}
\item Minimum outputs:
\begin{itemize}
\item Time used to calculate the positions for given n
\item Amount of threads/processors used
\item Calculated total amount of positions for given n (NO individual positions)
\end{itemize}
\end{itemize}
\begin{itemize}
\item Performance competition data set (problem size n) is 17. 
\begin{itemize}
\item in 2011  best time was 144 s (Java)
\end{itemize}
\end{itemize}
\end{itemize}

\begin{thebibliography}{9}

\bibitem{aaaaa}
TÄHÄN SITTEN MEIDÄN TYÖSSÄ KÄYTETTÄVÄT LÄHTEET!\\ SAMAAN TYYLIIN KU NOI, JOTKA OTETAAN SITTEN POIS...

\bibitem{Casey}
Casey, John (1886). A sequel to the first six books of the Elements of Euclid.\\ Luettu 22.9.2011. Saatavissa: http://www.archive.org/details/americana

\bibitem{Cool}
Coolidge, Julian (1916). A Treatise on the Circle and the Sphere. Luettu 21.9.2011. Saatavissa: http://www.archive.org/stream/treatiseoncircle00cooluoft\#page/166/\\
mode/2up/search/apollonius

\bibitem{Dörrie}
Dörrie, Heinrich (1965). 100 Great Problems of Elementary Mathematics:\\ Their History and Solutions, sivut: 154-160. Luettu 6.10.2011.\\ Saatavissa: http://www.scribd.com/doc/25259960/\\100-Great-Problems-of-Elementary-Mathematics-Dover-Tqw-darksider


\end{thebibliography}

\end{document}
